---
title: "Lab 00 - Hello IDS!"
author: "Kate Robinson"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Kate", "Connor", "Ruth", 
           "Kate", "Torgua", "Ellie"),
  github_username = c("kateh-robinson", "cburnett-123", "r-u-th", 
                      "katef26", "torgua", "elliesmith1406"), 
  colour = c("green", "orange", "green", 
             "pink", "green", "blue"),
  hobby = c("singing", "guitar", "sewing", 
            "badminton", "minecraft", "basketball"),
  favourite_number = c(4, 6, 7, 6, 8, 6)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```

A bar chart with each bar as our git hub username, each bar of height favourite number, and each bar's colour is our favourite colour.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Usernames", 
          y = "Favourite number",
          title = "IDS Team Info")
```

labs() labels the x and y axes and gives the bar plot a title.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

Could use a word cloud or only look at the most popular hobbies.
